Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-10-01 final_submission/manuscript.tex
figures in

\subsection{Predictions}
	//TODO
% \subsection{Validation and Robustness Testing}
% 	//TODO
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO

>>>>

\subsection{Predictions}
	Running the $sir_{04}.m$ script to solve the system of ODE's for the segmented SIR model with equal distribution of vaccines produces the following plots:

    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{figures/ryan_plot_01.png}
    \end{figure}
    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{figures/ryan_plot_02.png}
    \end{figure}
    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{figures/ryan_plot_03.png}
    \end{figure}
    \begin{figure}[H]
    \centering
        \includegraphics[width=\textwidth]{figures/ryan_plot_04.png}
    \end{figure}

    The fraction of deaths remains small for all populations so it is not plotted. The total number of person-months of suffering is the integral of the green curve.
% \subsection{Analysis of Model (robustness)}
% 	//TODO
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO
